\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-05-01 evaluation.tex
add title page and convert to book format
random shit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Evaluation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsection{User Experience}

@@

\subsubsection{Time Breakdown}

@@

\subsubsection{Descriptive Feedback}
\label{sec:eval-feedback}

@@

The following feedback pertains to the user interface.
For Landslide to be appealing as a debugging tool, we should improve the user interface (or the infrastructure, in some cases) to address these issues.

@@

@@

\subsubsection{Landslide Victories}
% TODO
% nadim - wait bug (claimed easy to spot with code review)
% margaret/echo - ds assertion bug
% margaret/echo - vanish c_s return idle bug; helped find when idle was running when shouldn't be
% tpassaro found double free, but deterministic
% apodolsk found no bugs because no hello world
% pjumde's group found no bugs..?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Bug Case Studies}
\label{sec:eval-casestudy}

\subsubsection{Bug Descriptions}

@@

\subsubsection{Numbers}
\label{sec:eval-numbers}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Summary of Bugs Found}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Discussion}

\subsubsection{Invariants}

@@

\subsubsection{Recommended Testing Strategies}
\label{sec:discussion-strategies}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Evaluation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{User Experience}

@@

\subsection{Time Breakdown}

@@

\subsection{Descriptive Feedback}
\label{sec:eval-feedback}

@@

\subsubsection{User Interface Feedback}

For Landslide to be appealing as a debugging tool, we should improve the user interface (or the infrastructure, in some cases) to address the following issues.

@@

\subsubsection{Technical Feedback}

@@

\subsection{Landslide Victories}
% TODO
% nadim - wait bug (claimed easy to spot with code review)
% margaret/echo - ds assertion bug
% margaret/echo - vanish c_s return idle bug; helped find when idle was running when shouldn't be
% tpassaro found double free, but deterministic
% apodolsk found no bugs because no hello world
% pjumde's group found no bugs..?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Bug Case Studies}
\label{sec:eval-casestudy}

\subsection{Bug Descriptions}

@@

\subsection{Numbers}
\label{sec:eval-numbers}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary of Bugs Found}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

\subsection{Invariants}

@@

\subsection{Recommended Testing Strategies}
\label{sec:discussion-strategies}

### 2012-05-01 terminology.tex
add title page and convert to book format
random shit

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Terminology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:terminology}

In this section we define certain terms that have specific meanings in the context of Landslide.

\subsection{Basic Terms}

\begin{enumerate}
	\item {\bf Guest kernel}:
		The kernel which is being tested for concurrency bugs by Landslide.
	\item {\bf Test case}:
		Abstractly, the set of inputs under which the guest kernel is tested. Practically, a user-space program which runs on top of the guest kernel to execute a particular set of system calls, while Landslide performs systematic exploration
\suspend{enumerate}

\subsection{Scheduling Terms}

@@

\subsection{Systematic Exploration Terms}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Terminology}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:terminology}

In this chapter we define certain terms that have specific meanings in the context of Landslide.

\section{Basic Terms}

\begin{enumerate}
	\item {\bf Guest kernel}:
		The kernel which is being tested for concurrency bugs by Landslide.
	\item {\bf Test case}:
		Abstractly, the set of inputs under which the guest kernel is tested. Practically, a user-space program which runs on top of the guest kernel to execute a particular set of system calls, while Landslide performs systematic exploration.
\suspend{enumerate}

\section{Scheduling Terms}

@@

\section{Systematic Exploration Terms}
